Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System

### 2022-12-05 paper-kelompok/main.tex
Minor changes

\author{\IEEEauthorblockN{
    Alzana Armaniar Farhani\IEEEauthorrefmark{1},
    Balkan Khilmi Assakandari\IEEEauthorrefmark{2},
    Anindhita Nayazirly\IEEEauthorrefmark{3}, \\
    Akhmadi Surawijaya\IEEEauthorrefmark{4},
    Muhammad Ogin Hasanuddin\IEEEauthorrefmark{5}}
\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
\textit{School of Electrical Engineering and Informatics} \\
\textit{Institut Teknologi Bandung}\\
Bandung, Indonesia \\
\IEEEauthorrefmark{1}farhanialzana@gmail.com,
\IEEEauthorrefmark{2}balkankhilmi@gmail.com,
\IEEEauthorrefmark{3}zirlysukarno@gmail.com,
email,
email
}
}

@@

\section{Conclusions}
To support the study of spectrophotometry analysis in DMF platform, we describe the assembly of a portable spectrophotometer that can be integrated with a particular DMF system.
The portability makes on-the-go research processes easier.
Data acquisition, storage, and user experience is made simpler by our developed portable visible spectrophotometer and a user-friendly interface.
Measurement's accuracy of red, blue, and yellow food dyes and its repeatability demonstrated good performances in experimental validation versus commercial spectrophotometer (Evolution 220 by Thermo Fisher Scientific).
The colorimetrice glucose assay (maximum of absorbance at 540 nm) measurements were comparable but quite inferior; these issues could be resolved by ...
Future work will focus on...

>>>>

\author{\IEEEauthorblockN{
    Alzana Armaniar Farhani\IEEEauthorrefmark{1},
    Balkan Khilmi Assakandari\IEEEauthorrefmark{2},
    Anindhita Nayazirly\IEEEauthorrefmark{3}, \\
    Akhmadi Surawijaya\IEEEauthorrefmark{4},
    Muhammad Ogin Hasanuddin\IEEEauthorrefmark{5}}
\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
\textit{School of Electrical Engineering and Informatics} \\
\textit{Institut Teknologi Bandung}\\
Bandung, Indonesia \\
\IEEEauthorrefmark{1}farhanialzana@gmail.com,
\IEEEauthorrefmark{2}balkankhilmi@gmail.com,
\IEEEauthorrefmark{3}zirlysukarno@gmail.com,
\IEEEauthorrefmark{4}asurawijaya@itb.ac.id,
\IEEEauthorrefmark{5}moginh@itb.ac.id
}
}

@@

\section{Conclusions}
To support the study of spectrophotometry analysis in DMF platform, we describe the assembly of a portable spectrophotometer that can be integrated with a particular DMF system.
The portability makes on-the-go research processes easier.
Data acquisition, storage, and user experience is made simpler by our developed portable visible spectrophotometer and a user-friendly interface.
Measurement's accuracy of red, yellow, and blue food dyes and its repeatability demonstrated good performances in experimental validation versus commercial spectrophotometer (Evolution 220).
The colorimetric glucose assay (maximum of absorbance at 540 nm) measurements were comparable but quite inferior; these issues could be resolved by retesting the colorimetric reactions more thoroughly.
Future work will focus on designing a better voltage regulation and heat insulation for the lamp, as well as designing reducing movable parts from the light path configuration.
